---
title: "da-ws-06-2"
author: "Jannis Gottwald, Lukas Ditzel, Michaela Vorndran, Maite Lezama Valdes, Alexander Jorns"
date: "27 November 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## W06-2: Wheat vs. barley revisited

####task: 
assess prediction performance winter barley yield based on yield numbers 
winter wheat by biv lin model. cross-validation: mean of the root mean 
square error, its minimum, 25% 50% and 75% quantile and maximum value across 
the cross-validation runs.

```{r}
#da-ws-06-2
source("GitHub/data/data_analysis/data/rdata/path_da.R")

#root mean sqare error implemented in function rmse() in this package:
#install.packages("hydroGOF")
library(hydroGOF)

cp <- readRDS(paste0(path_da_rds,"feldfr_clean.rds"))

#vector logical: na-values in rows?
row.has.na <- apply(cp[,c(7,9)], 1, function(n){any(is.na(n))})
sum(row.has.na)
#test how many cases remain
nrow(cp)-sum(row.has.na)
x <- cp[!row.has.na,]

lmt82 <- lapply(seq(100), function(n){
  set.seed(n)
  s1 <-sample(nrow(x), 0.8*nrow(x))
  traindata <- x[s1,]
  testdata <- x[-s1,]
  mod <- lm(Winter_wheat~Winter_barley, data=traindata)
  pred <- predict(mod, newdata = testdata)
  obsv <- testdata$Winter_wheat
  modrmse <- rmse(pred,obsv)
  model_r_squared <- summary(mod)$r.squared
  dflmt = data.frame(modrmse=modrmse, r_sq = model_r_squared,
                     pred=pred, obsv=obsv)
  dflmt
})
dflmt <- do.call("rbind", lmt82)
#rownames(dflmt) <- c(1:100)
head(dflmt)
summary(dflmt[,1])
boxplot(dflmt[,1])
```

####Prediction performance: The root mean sqare error (the error being the deviation 
####between observed and predicted values) ranges in any repetition of the 100 random
####samples between about 7.3 and 8 (depending on the sample selection) and is more or less normal distributed. 

```{r}
#assess distribution of dependent variable prediction
summary(dflmt$pred)
mean(dflmt$pred)
sd(dflmt$pred)

#assess distribution of dependent variable observation
summary(dflmt$obsv)
mean(dflmt$obsv)
sd(dflmt$obsv)

boxplot(dflmt$pred, dflmt$obsv, names=c("predicted", "observed"))
```

####The range of observed values in the dependent variable in this case is from 0 to 113.3, and 14.67
####to 119.6 in this case of selection, its mean being 71.95 with a SD of 12.69 in case
####of predicted values respectively 71.95 and 10.2. So the maximum error to be 
####expected seems to be acceptable.
####Although interquartil range in predicted values is smaller than in the actual
####distribution, as can be seen in the boxplots, observed and predicted distributions
####of winter wheat can be predicted nicely with help of winter barley.

