---
title: "rs-ws-03-2"
author: Jannis Gottwald, Lukas Ditzel, Michaela Vorndran, Maite Lezama Valdez, Alexander
  Jorns,
date: "09 November 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Strategy
- neighbouring raster cells are most likely part of the same landuse category
- neighbouring tiles should share landuse categories at theire neighbouring edges
- the results of mathematical operations like divisions should be close to one if the data sets are    similar, so does the mean of the above operations
- we devided neighbouring rows ore columns (depending on where the tiles where connected) and took the mean of these devisions
- The results show that the values of the raster cells of two neighbouring tiles are very similar if they where taken from the same landuse category
-no further processing is needed



```{r, eval=FALSE}
library(raster)
install.packages("tools")
library(tools)


path_main<-("C:/Users/Jannis/Documents/GitHub/msc_phygeo_class_of_2016/remote_sensing_2016")
path_c<-paste0(path_main, "/data/raster/cross_check/")
path_results<-paste0(path_main, "/results/rs-ws-03-2/")


read<-list.files( recursive=TRUE, pattern=glob2rx("*.tif"), full.names=TRUE)

ngb_aerials <- function(aerial_files, step = 2000){
  
  ngb_files <- lapply(basename(aerial_files), function(act_file){
    
    # Get names without path to compare names although path might be different
    act_ext <- file_ext(act_file)
    fnames <- basename(aerial_files)
    
    # Get x and y coordinates of actual file from filename
    act_file_x <- as.numeric(substr(act_file, 1, 6))
    act_file_y <- as.numeric(substr(act_file, 8, 14))
    
    # Set neighbours starting from north with clockwise rotation (N, E, S, W)
    pot_ngb <- c(paste0(act_file_x, "_", act_file_y + step, ".", act_ext),
                 paste0(act_file_x + step, "_", act_file_y, ".", act_ext),
                 paste0(act_file_x, "_", act_file_y - step, ".", act_ext),
                 paste0(act_file_x - step, "_", act_file_y, ".", act_ext))
    
    # Check if neighburs exist and create vector with full filepath
    act_ngb <- sapply(pot_ngb, function(f){
      pos <- grep(f, fnames)
      if(length(pos) > 0){
        return(aerial_files[pos])
      } else {
        return(NA)
      }
    })
    return(act_ngb)
  })
  
  names(ngb_files) <- aerial_files
  return(ngb_files)
  
}

neighb<-ngb_aerials(read)
y<-NULL
z<-NULL

for (i in seq(neighb)){if(!is.na(neighb[[i]][[1]]))
{
  x <-stack(names(neighb[i]))
  
  n<-stack(basename(neighb[[i]][1]))
  
  y<-mean((x[1,])/(n[nrow(n),]))
  
  z<-c(z,y)
  
}}

for (i in seq(neighb)){if(!is.na(neighb[[i]][[2]]))
  
{
  x <-stack(names(neighb[i]))
  
  e<-stack(basename(neighb[[i]][2]))
  
  y<-mean((x[,ncol(x)])/(e[,1])) 
  
  z<-c(z,y)
  
}}

for (i in seq(neighb))
{
  if(!is.na(neighb[[i]][[3]]))
  { 
    x <-stack(names(neighb[i]))
    
    s<-stack(basename(neighb[[i]][3]))
             
             y<-mean((x[nrow(x),])/(s[1,]))
             
             z<-c(z,y)
  }}

for (i in seq(neighb))
{
  if (!is.na(neighb[[i]][[4]])) 
  {
    x <-stack(names(neighb[i]))
    
    w<-stack(basename(neighb[[i]][4]))
    
    y<-mean((x[,1])/(w[,ncol(w)])) 
            
            z<-c(z,y) }}


saveRDS(z, file=paste0(path_results,"rdata/rs-ws-03-2.rds"))



```

## Including Plots

You can also embed plots, for example:

```{r }
# Executable section
# Set path ---------------------------------------------------------------------
path_main<-("C:/Users/Jannis/Documents/GitHub/msc_phygeo_class_of_2016/remote_sensing_2016")
path_c<-paste0(path_main, "/data/raster/cross_check/")
path_results<-paste0(path_main, "/results/rs-ws-03-2/")
if(Sys.info()["sysname"] == "Windows"){
  filepath_base <- path_main
} else {
  filepath_base <- "/media/permanent/active/moc/msc-phygeo-remote-sensing-2016/"
}

path_data <- paste0(filepath_base, "data/")
path_rdata <- paste0(path_results, "rdata/")

# Load intermediate results which form the basis for the descriptive analysis --
results <- readRDS(file = paste0(path_results, "rdata/rs-ws-03-2.rds"))


# Perform final descriptive analysis -------------------------------------------
# ...

boxplot(results)
```
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
